% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rishi Shah 
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
\usepackage{chngpage}
\usepackage{array}
%\usepackage[colorlinks]{hyperref}
\usepackage[colorlinks,urlcolor=blue,linkcolor=blue,anchorcolor=black,citecolor=black,filecolor=blue,runcolor=blue]{hyperref}

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\newcommand{\tabincell}[2]{\begin{tabular}{@{}#1@{}}#2\end{tabular}}

\name{Tianyu Wang} % Your name
%\address{156 Kasturi, Balajinagar, Sangli 416416} % Your address
%\address{123 Pleasant Lane \\ City, State 12345} % Your secondary addess (optional)
\address{(+86)18258882697 \\ wtyatzoo@zju.edu.cn} % Your phone number and email

\begin{document}

\begin{rSection}{Profile}
I currently work as a research assistant for Prof. Jin Huang, State Key Lab of CAD\&CG, Zhejiang University. My research interest is character animation and video game development.
\end{rSection}

\begin{rSection}{Education}

{\bf Zhejiang University, Hangzhou, China} \hfill {\em September 2016 - Present} 
\\ M.Eng. in Computer Science\hfill {Advisor: Prof. Jin Huang} 
%\\ Department of Structural Engineering\\
\\{\bf Sichuan University, Chengdu, China} \hfill {\em September 2012 - June 2016} 
\\ B.Eng. in Computer Science\hfill { Overall GPA: 81.54/100 }

\end{rSection}

\begin{rSection}{Publication}
Jiong Chen, Hujun Bao, \textbf{Tianyu Wang}, Mathieu Desbrun, Jin Huang: Numerical Coarsening using Discontinuous Shape Functions. \emph{ACM Transaction Graphics 37(4)(SIGGRAPH 2018)}, Vancouver, Canada, 2018
\end{rSection}


\begin{rSection}{Research Experience}

  \begin{rSubsection}{Research Assistant,State Key Lab of CAD\&CG,ZJU}{September 2016 - present}
    {Advisor: Prof. Jin Huang}{See below project section for details}
  \end{rSubsection}

\end{rSection}

\begin{rSection}{Honors and Awards}
  \textbf{Graduate of Merit/Triple A graduate}, Zhejiang University, 2018\\
  \textbf{Award of Honor for Graduate}, Zhejiang University, 2018\\
  \textbf{Wen Chixiang Scholarship}, Zhejiang University, 2018\\
  \textbf{Silver Medal}, ACM-ICPC China Provincial Programming Contest, Chengdu Site, 2013 and 2014\\
  \textbf{2nd University Scholarship}, Sichuan University, 2013
\end{rSection}

%\newpage
\begin{rSection}{Skills}
\begin{tabular}{ @{} >{\bfseries}l @{\hspace{4ex}} l }
Languages \ & C/C++,Python,Latex,Java \\
Toolkit  & \tabincell{l}{Eigen,Boost,NumPy,Tensorflow,OpenGL,OpenCV,CUDA,OpenMP,ParaView,\\GIMP,Inkscape,CMake(Linux),Git,SVN}\\
Platforms&Linux 16.04
\end{tabular}

\end{rSection}

\iffalse
\begin{rSection}{Academic Achievements} 
 Runners up in B.G.Shirke Vidyarthi Competition for Innovative Project organized by Pune Construction Engineering Research Foundation in January 2018
\item Won First Prize in Model Making Competition Organized by Symbiosis Institute of Technology, Pune.
\end{rSection}
\fi



\begin{rSection}{Extra-Cirrucular} \itemsep -3pt
\item I love basketball and play as a point guard skilled in shooting!
\item I love film and TV series and write film review on movie.douban.com!
\end{rSection}

\iffalse
\begin{rSection}{Personal Traits}
\item Highly motivated and eager to learn new things.
\item Strong motivational and leadership skills.
\item Ability to work as an individual as well as in group.
\end{rSection}
\fi

\end{document}
